Enhanced proximity effect in zigzag-shaped Majorana Josephson junctions.

### 2019-02-26 paper/snakemajoranas.tex
rewrite more of the last paragraph of Sec IV

\comment{In a straight system, the Majoranas are very poorly localized.}
For the straight system [Fig.~\ref{fig:wave_functions}(a)], we see that the decay of the density is long compared to the system size.
The wave function extends to the center of the system, resulting in highly overlapping Majoranas and a non-zero energy of the state.
Further, the energy of the Majorana state $E_\textrm{M}$ in the straight system is high in comparison with the topological gap $E_\textrm{gap}$.
Altogether, the small topological gap, but also the before mentioned high velocity, result in poorly localized Majoranas and minimal topological protection against perturbations.  % TODO: probably put the eq for coherence length here?

\comment{In a zigzag geometry Majoranas are localized within one segment of zigzag independent of details}
We observe that for zigzag systems the Majorana properties improve independent of the details of the specific geometry.
All of the zigzag type geometries display a significantly reduced Majorana size which improves the localization of the Majorana wave functions as is visible in the density plots.
The Majorana size $\xi_\textrm{M}$ improves by a factor ~70 and is localized within one segment of the zigzag.
Further, the topological gap is an order of magnitude lower, and as mentioned in section \ref{sec:band_structures}, this can be attributed to the way the energy gap and velocity factor into the Majorana coherence length which scales with these parameters $\xi_\textrm{M}=\hbar v_\textrm{F} / \Delta_\textrm{ind}$.
Additionally, the reduction of the Majorana size allows for shorter systems sizes, which is favorable because in an experimental device the coherence length of a material sets a limit for the device size.

>>>>

\comment{In a straight system, the Majoranas are very poorly localized.}
For the straight system [Fig.~\ref{fig:wave_functions}(a)], we see that the decay of the density is long compared to the system size.
The wave function extends to the center of the system, resulting in highly overlapping Majoranas and a non-zero energy of the state.
Further, the energy of the Majorana state $E_\textrm{M}$ in the straight system is high in comparison with the topological gap $E_\textrm{gap}$.
Altogether, the small topological gap, but also the before mentioned high velocity, result in poorly localized Majoranas and minimal topological protection against perturbations because

\begin{equation}
\label{eq:xi_M}
\xi_\textrm{M}=\hbar \frac{v_\textrm{F}}{\Delta_\textrm{ind}}.
\end{equation}

\comment{In a zigzag geometry Majoranas are localized within one segment of zigzag independent of details}
We observe that for zigzag systems the Majorana properties improve independent of the details of the specific geometry.
All of the zigzag type geometries display a significantly reduced Majorana size which improves the localization of the Majorana wave functions as is visible in the density plots.
The Majorana size $\xi_\textrm{M}$ improves by a factor ~70 and is localized within one segment of the zigzag.
Further, the topological gap is an order of magnitude higher, and as mentioned in section \ref{sec:band_structures}, the velocity is an order of magnitude lower.
Both of these parameters ensure that $\xi_\textrm{M}$ is greatly improved (Eq.~\eqref{eq:xi_M}).
Finally, the reduction of the Majorana size allows for shorter systems sizes, which is favorable because in an experimental device the coherence length of a material sets a limit for the device size.
